---
title: "Quick Start"
author: "Shu Fai Cheung"
date: "`r Sys.Date()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(semlbci)
```

# Introduction

This package includes functions for finding the likelihood based confidence intervals of parameters in the fitted object of a structural equation modeling (SEM) function. Currently, it only supports the output from `lavaan`.

# Limitations

This package is still in its early development (pre-alpha). These are the limitations:

- It only supports single-sample SEM. It *may* work for multiple-sample SEM but this has not been tested.

- It only supports model fitted by maximum likelihood (ML) estimation, including full information maximum likelihood (FIML).

- It uses the method by Neales and Miller (2012) but can not yet check whether a parameter is near its boundary. Nevertheless, a post-search test will be done by `lavaan` to check whether the final solution after finding a confidence limit is admissible.

