---
title: "Internal Workflow of semlbci()"
author: "Shu Fai Cheung"
date: "`r Sys.Date()`"
bibliography: semlbci_technical_references.bib
csl: apa.csl
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r echo = FALSE}
library(DiagrammeR)
```

# Introduction

This vignette is a simplified version of the
[technical appendix](https://osf.io/q6e3h)
hosted at the [OSF project site](https://osf.io/b9a2p/)
of Cheung and Pesigan (2023), associated with the package
[`semlbci`](https://sfcheung.github.io/semlbci/).
It presents the workflow used by
`semlbci::ci_i_one()` and `semlbci::ci_bound_wn_i()`
to find a bound of a likelihood-based confidence interval
(LBCI) of a parameter in a fitted `lavaan` model.

`semlbci::ci_i_one()` and `ci_bound_wn_i()`
are internal functions used by
`semlbci::semlbci()`. They are not supposed to be used by
users. Nevertheless, developers can
use them directly if so desired.

# Purposes of the Functions

`semlbci::ci_i_one()` is called by `semlbci::semlbci()`
for each confidence bound (limit), twice for each selected
parameter, once for the lower bound and once for the
upper bound. It sets up necessary arguments and then
call the lowest level function responsible for searching
a bound.

Currently, only one such function is available,
`semlbci::ci_bound_wn_i()`, which implements the
algorithm proposed by @wu_adjusted_2012,
adapted by @pek_profile_2015, without the part for
handling parameters with attainable bounds. To avoid
confusion with the method by @wu_adjusted_2012
for parameters with attainable bound,
we denote this method WNPW (Wu-Neale-Pek-Wu)
method in this document.

# Overall Workflow

We first present the overall workflow[^note_on_flow] of
`semlbci::semlbci()`. We then present the workflow
of `semlbci::ci_i_one()`, called by `semlbci::semlbci()`
once for each bound of each parameter requested (twice for
each parameter, once for the lower bound and once for
the upper bound). Last, we present the workflows of
the two stages of `semlbci::ci_bound_wn_i()`, the
minimization stage and the checking stage.

Details for the arguments mentioned in this section
can be found from the help pages of `semlbci::semlbci()`,
`semlbci::ci_i_one()`, and `semlbci::ci_bound_wn_i()`.

[^note_on_flow]: Some steps are omitted for readability.

## `semlbci::semlbci()`

`semlbci::semlbci()` is the main function used by users.
It is used to find the LBCI of selected parameters. It is
also responsible for setting the equality constraint
required by the WNPW method. If robust LBCI
proposed by @falk_are_2018 is requested, it will also
compute the
scaling and shift factors to be used by the robust
likelihood ratio test by @satorra_scaled_2000.

The general workflow of `semlbci::semlbci()` is shown
below:


```{r fig-semlbci, fig.cap = "General Workflow of `semlbci::semlbci()`", echo = FALSE, fig.align = "center"}
mermaid("
graph TD
  classDef default fill:#DADBFF;
  A[\"Is <code>check_fit</code> <code>TRUE</code>?\"]
  A -- Yes --> AYes[\"Are the model and<br/>estimation method supported?<br/>(Checked by <code>check_sem_out()</code>)\"]
  A --No--> B
  AYes -- No --> AYesNo[\"Terminate and raise an error\"]
  AYes --Yes--> B
  B[\"Find the ids of parameters requested\"]
  B --> C
  C[\"Call <code>set_constraint()</code> to set the equality constraint<br/>used by the WNPW method\"]
  C --> D
  D[\"Robust LBCI requested?\"]
  D -- Yes --> DYes
  DYes[\"For each parameter,<br/>call <code>scaling_factor3()</code><br/>to compute the scaling and shift factors\"]
  D -- No --> E
  DYes --> E
  E[\"Call <code>ci_i_one()</code> once for<br/>each bound of each parameter\"]
  E --> F
  F[\"Combine the bounds to form the confidence intervals<br/>and return the results\"]
", height = 840, width = 650)
```


We describe below the two functions called by `semlbci::semlbci()` in
the workflow, `semlbci::set_constraint()` and `semlbci:::scaling_factor3()`.

### `semlbci::set_constraint()`

This function, called by `semlbci::semlbci()`, is used to
set the equality constraint used by
the WNPW method.

As presented in @pek_profile_2015, to find the lower bound,
$\theta_L$, of the 100(1-$\alpha$)% LBCI of $\hat{\theta}_j$,
$\theta_L$ is minimized with respect to all parameters,
$(\theta_L, \boldsymbol{\theta}_q)$, $\boldsymbol{\theta_q}$ being all parameters
other than $\theta_L$, subject to the following constraint:

$$
0 = 2nF(\theta_L, \boldsymbol{\theta_q}) - (2nF(\hat{\theta}) + \chi_{(1, 1 - \alpha)}^2)
$$

$F(\hat{\boldsymbol{\theta}})$ is the value of the discrepancy function
evaluated at the ML estimate $\hat{\boldsymbol{\theta}}$.
$\chi_{(1, 1 - \alpha)}^2$ is the $\chi^2$ critical value at
$df = 1$ and level of significance = $\alpha$
(about 3.84 with $\alpha = .05$), and $n$ is the sample size
(total sample size in multisample models).

This constraint means that model $\chi^2$ difference test
between the model with $\theta_j$ fixed to $\theta_L$
and the original model with $\theta_j$ freely estimated
should have a *p*-value equal to $\alpha$.

In `lavaan`, $F(\theta_L, \boldsymbol{\theta}_q)$ is `"fmin"` in the
output of `lavaan::fitMeasures()`. When the estimator is `ML` and
`likelihood = "normal"`, the default, multiplying `"fmin"`
by $2n$ yields the model $\chi^2$.

To find the upper bound, $\theta_U$, $-\theta_U$ is
minimized (equivalently, $\theta_U$ is maximized). The
final value will be multiplied by $-1$ to get the upper bound.

The WNPW method can easily be used when a model
has one or more equality constraints on the parameters.
These constraints
are simply extracted from the `lavaan` object and
passed to `nloptr::nloptr()`, the function used
to do the minimization,
along with the
constraint by the WNPW method when minimizing
the objective function.

The function `semlbci::set_constraint()` returns a general
version of the constraint:

$$
0 = 2nF(\theta_L, \boldsymbol{\theta}_q) - (2nF(\hat{\boldsymbol{\theta}}) + \frac{\chi_{(1, 1 - \alpha)}^2 - b}{a})
$$

In this general form, $a$ is the scaling factor and $b$ is
the shift factor. When $a = 1$ and $b = 0$, it is the
constraint in the WNPW method. When robust LBCI
is requested, the scaling and shift factors are computed
as in the same way by `lavaan::lavTestLRT()` with
`method = satorra.2000` and `A.method = "exact"`.[^sf]

[^sf]: Internally, `sf = a^(-1)` is stored. To
be consistent with `T_3` presented in @asparouhov_simple_2010,
we used `a` instead of `a^(-1)` in the equation in this
document.

### `semlbci:::scaling_factors3()`

This internal function, not exported, computes the
scaling and shift factors used by `lavaan::lavTestLRT()`
with `method = satorra.2000` and `A.method = "exact"`.
This is the method proposed by @falk_are_2018 for robust
LBCI. These factors can be used to do the robust
likelihood ratio test proposed by @satorra_scaled_2000
without directly calling `lavaan::lavTestLRT()` when
doing the minimization. Because these factors depend only
on the parameter for which the LBCI is to be searched, they
can be computed once and reused during the minimization.

Since version 0.6-13 of `lavaan`, `lavaan::lavTestLRT()`
stores the
scaling and shift factors in the output. Therefore, for
future versions of `semlbci`, it is possible to remove
`semlbci:::scaling_factor3()` and use `lavaan::lavTestLRT()`
to get the scaling and shift factors directly.

## `semlbci::ci_i_one()`

The workflow of `semlbci::ci_i_one()` is presented below:


```{r fig-ci-i-one, fig.cap = "General Workflow of `semlbci::ci_i_one()`", echo = FALSE, fig.align = "center"}
mermaid("
graph TD
  classDef default fill:#F8DAFF;
  B[\"Robust LBCI requested?\"]
  B -- Yes --> C[\"Scaling and shift factors (<code>sf_full</code>)<br/>supplied by <code>semlbci()</code>?\"]
  C -- No --> D[Compute scaling and shift factors]
  D --> E
  C -- Yes --> E[\"Call <code>ci_bound_wn_i()</code>\"]
  B -- No --> E
  E --> F[\"<code>status</code> == 0?\"]
  F -- No --> G[\"Move the lower bounds<br/>of free variances closer to zero<br/>and call <code>ci_bound_wn_i()</code> again\"]
  F -- Yes --> ZZ[\"Return the results to <code>semlbci()</code><br/>Bound set to <code>NA</code> if status != 0\"]
  G --> H[\"<code>status</code> == 0?\"]
  H -- Yes --> ZZ
  H -- No --> I[\"Is <code>try_k_more_times</code> > 0?\"]
  I -- No --> ZZ
  I -- Yes --> J[\"Reduce the tolerance for convergence<br/>(Reduce <code>xtol_rel</code> and <code>ftol_rel</code>)\"]
  J --> K[\"Call <code>ci_bound_wn_i()</code>\"]
  K --> L[\"<code>status</code> == 0?\"]
  L -- Yes --> ZZ
  L -- No --> M[\"Tried<br/><code>try_k_more_times</code>?\"]
  M -- No --> J
  M -- Yes --> ZZ
", height = 1300, width = 700)
```


Its job is to call `semlbci::ci_bound_wn_i()`
once or more than once to find the bound of an LBCI of
a parameter. It does not check the validity or plausibility
of the bound. The lowest level function, `semlbci::ci_bound_wn_i()`,
is responsible for doing the checks. If something is wrong,
`semlbci::ci_bound_wn_i()` will set `status` to a non-zero
value.

The argument `try_k_more_times` is used to determine whether
it will try "harder" for *k* more times if the first attempt
failed (e.g., `status != 0`, meaning that the bound found
fails one or more checks).

## `semlbci::ci_bound_wn_i()`

The function `semlbci::ci_bound_wn_i()` is the lowest level
function that is responsible for searching the bound. It implements
an optimization method (the WNPW method in this case)
and takes care of all the technical details. It is not
supposed to be used by users and the interface is not designed
to be user-friendly. Nevertheless, interested users can use
it directly to find a bound, bypassing `semlbci::semlbci()`.
Examples can be found in
`vignette("technical_searching_one_bound", package = "semlbci")`.

The workflow of `semlbci::ci_bound_wn_i()` can be separated into
two stages, the *minimization stage* and the *checking stage*.

### Minimization Stage

The workflow of the minimization stage is presented below:


```{r fig-ci-i-bound-wn-i-min, fig.cap = "Workflow of `semlbci::ci_bound_wn_i()` - Minimization Stage", echo = FALSE, fig.align = "center"}
mermaid("
graph TD
  classDef default fill:#DAFFDA;
  A[\"Store the point estimates and Wald or Delta CI\"]
  A --> B[\"Define the function to be minimized [<code>lbci_b_f()</code>]<br/>and the gradient function of this function [<code>lbci_b_grad()</code>]\"]
  B --> C[\"Is <code>wald_ci_start</code> TRUE?\"]
  C -- Yes --> CYes[\"Call <code>set_start_wn()</code><br/>to set the starting values<br/>based on Wald or Delta CI\"]
  C -- No --> CNo(\"Slighly pertubate<br/>the point estimates<br/> to set the starting values\")
  CYes --> D[\"Set the lower bounds of free variances<br/>to a small positive value\"]
  CNo --> D
  D --> E[\"Call <code>>nloptr::nloptr()</code> to minimize the objective function,<br/>with the equality constraint <code>f_constr</code><br/>(created by <code>set_constraint()</code>)\"]
  E --> F[\"Pass the results to the Checking Stage\"]
", height = 650, width = 500)
```


#### Optimization Algorithm

The function used to do the minimization
is `nloptr::nloptr()`, using `NLOPT_LD_SLSQP` as the value for `algorithm`.
The parameters (`x0`) are all free parameters in the model. The objective
function, `eval_f` is set to `lbci_b_f()`, the function that returns
the bound in each iteration. The gradient function, `eval_grad_f`, is
`lbci_b_grad()`. The equality constraint(s), `eval_g_eq`, is the result
of `set_constraint()`, supplied through the argument `f_constr` from
`semlbci::semlbci()`, along with other equality constraints in the model,
if any.

The two functions created by `semlbci::ci_bound_wn_i()` in this stage,
`lbci_b_f()` and `lbci_b_grad()`, are described below.

##### `lbci_b_f()`

In the WNPW method, if the parameter, $\theta_j$,
is a free parameter, and the lower bound is to be searched,
this function simply returns the value of
$\theta_j$ (all other free parameters other than $\theta_j$
are denoted by $\theta_q$):

$$
f(\theta_j, \boldsymbol{\theta}_q) = \theta_j
$$

If the upper bound is to be searched, then this function is:

$$
f(\theta_j, \boldsymbol{\theta}_q) = -\theta_j
$$


If the parameter is a function of some free parameters (e.g.,
an indirect effect, or a standardized coefficient such as
correlation), denoted by $h(\boldsymbol{\theta})$, $\boldsymbol{\theta}$ being all
free parameters (though some may not be used in $h$), and
the lower bound is to be searched, then this function is:

$$
f(\boldsymbol{\theta}) = h(\boldsymbol{\theta})
$$

Similarly, if the upper bound is to be searched, this
function is:

$$
f(\boldsymbol{\theta}) = -h(\boldsymbol{\theta})
$$

Therefore, in the optimization, minimization is conducted
whether the lower or upper bound is to be searched.

##### `lbci_b_grad()`

The gradient of the object function, `lbci_b_f()`, is
either precomputed (if the parameter for which the bound
is being searched is a parameter)
or computed by `lavaan::lav_func_gradient_complex()`.

#### Tweaking the Optimization

The first attempt of optimization may fail, especially when
the target parameter is a function of free parameters (e.g., an
indirect effect, or a parameter in the standardized solution).
The arguments `xtol_rel`, `ftol_rel`, and
`lb` are adjusted across attempts. This is done by
`semlbci::ci_i_one()` for the second and subsequent calls to
`semlbci::ci_bound_wn_i()`.

### Checking Stage

The workflow of the checking stage is presented below:


```{r fig-ci-i-bound-wn-i-chk, fig.cap = "Workflow of `semlbci::ci_bound_wn_i()` - Checking Stage", echo = FALSE, fig.align = "center"}
mermaid("
graph TD
  classDef default fill:#FFE1DA;
  classDef statusNA fill:#ffdddd;
  class DNo,FNo,GNo statusNA
%%  DNo:::statusNA
%%  FNo:::statusNA
%%  GNo:::statusNA
  A[\"Which bound is requested?\"]
  A -- Upper --> AUpper[\"Multiply the value by -1\"]
  AUpper --> B[\"Store the value to <code>bound</code>\"]
  A -- Lower --> B
  B --> C[\"Initialize <code>status</code> to 0\"]
  C --> D[\"<b>Check <code>nloptr</code> Status</b>:<br/>Is status code from <code>nloptr</code> equal to 0?\"]
  D -- No --> DNo[\"Set <code>status</code> to 1\"]
  DNo --> F[\"<b>Check SEM Solution</b>:<br/>Is the <code>lavaan</code> results based on <code>nloptr</code> solution admissible?\"]
  D -- Yes --> F
  F -- No --> FNo[\"Set <code>status</code> to 1\"]
  FNo --> G[\"<b>Check the Achieved Level of Significance</b>:<br/>Is the <i>p</i>-value of the 1-<i>df</i> likelihood ratio test<br/>close enough to 1 - Confidence Level? (.05 for 95%)<br/>(<code>p_tol</code> used as the tolerance) (For robust LBCI, scaling and shift factors are used)\"]
  F -- Yes --> G
  G -- No --> GNo[\"Set <code>status</code> to 1\"]
  GNo --> E[\"Set <code>ci_limit_ratio</code> to the ratio of distances from the point estimate:<br/>(LBCI bound from point estimate) / (Wald or Delta bound to point estimate)\"]
  G -- Yes --> E
  E --> H[\"Is <code>status</code> equal to 0?\"]
  H -- No --> HNo[\"Set <code>bound</code> to <code>NA</code>\"]
  HNo --> I[\"Return the results\"]
  H -- Yes --> I
", height = 1200, width = 600)
```


It will do the following checks, in this order:

1. Is the status code of `nloptr::nloptr()` equal to 0 ("success")?

    If the status code of `nloptr::nloptr()` is not equal to 0,
    then the
    status code for `semlbci::ci_bound_wn_i()` will be set to 1.

2. In final solution, do the values of the free parameters result
  in an admissible solution? (Checked by `lavaan::lavInspect()` with
  `what = "post.check"`).

    The values of the parameters in the final solution is
    used to fit the model, and then `lavaan::lavInspect()`
    is called to check the solution. Examples of inadmissible
    solution are negative variances and correlations greater
    than one in magnitude.

    If the solution is not admissible, then the
    status code for `semlbci::ci_bound_wn_i()` will be set to 1.

3. When the target parameter (free or derived, i.e., the function
  of parameters, such as an indirect effect or a standardized
  regression coefficient) is fixed to the bound found, is the
  *p*-value of the likelihood ratio test between this
  constrained model and the original model equal to
  1 - confidence level (.05 for a 95% LBCI)?

    If not, then the likelihood-based confidence bound is
    by *definition* *invalid*. The
    status code for `semlbci::ci_bound_wn_i()` will be set
    to 1.

    The check is equivalent to using `lavaan::lavTestLRT()`.
    If robust LBCI is requested, then the check is equivalent
    to using `lavaan::lavTestLRT()` with
    `method = satorra.2000` and `A.method = "exact"`.

The bound is set to `NA` if the solution fails any of the
three checks presented above,
to prevent users from accidentally using a bound that
may be invalid.

In sum, the bound returned, if not `NA`, has the following
characteristics:

- Noted as "success" in the optimization by `nloptr::nloptr()`.

- The values of the parameters do not yield an inadmissible
    solution.

- The bound is *by definition* valid.

# Main Arguments

This section presents in details the arguments used by
`semlbci::ci_i_one()` and `semlbci::ci_bound_wn_i()`.

## `semlbci::ci_i_one()`

`semlbci::ci_i_one()` is an interface between user
functions such as `semlbci::semlbci()` and low level
functions such as `semlbci::ci_bound_wn_i()`. It
is responsible for setting necessary values to be used
by `semlbci::ci_bound_wn_i()`.

These are the main arguments of `semlbci::ci_i_one()`:

- `i`:

  The position (row number) of the target parameters
  as appeared in the parameter table of the output of
  `lavaan::lavaan()` and its wrappers, such as
  `lavaan::sem()` and `lavaan::cfa()`. This uniquely
  identifies a parameter, which can be free, fixed, or
  user-defined.

- `which`:

  Either `"lbound"` or `"ubound"`, denoting
  lower bound and upper bound, respectively. The confidence
  bound (limit) to be searched.

- `sem_out`:

  A `lavaan`-class object. the output of
  `lavaan::lavaan()` and its wrappers, such as
  `lavaan::sem()` and `lavaan::cfa()`.

- `method`:

  The method to be used to find a confidence
  bound. Currently, only the modified Wu-Neale method
  presented by Pek and Wu (2015) is supported (`"wn"`).
  Separating the low level function from this function
  allows for the possibility to develop low level functions
  for other methods, without the need to change the
  interface implemented in `semlbci::ci_i_one()`.

- `standardized`:

  Logical. Whether the confidence bound
  of the parameter in the standardized solution is to be
  searched. For example, for a covariance, whether the
  covariance, or the correlation, is to be used in searching
  the bound. Default is `FALSE`.

- `robust`:

  Whether robust likelihood-based confidence
  bound is to be searched, and if yes, the method to be used.
  Currently only support `"none"` (robust method not used)
  or `"satorra.2000"`, proposed by @falk_are_2018.

- `sf_full`:

  Used when `robust` is `"satorra.2000"`. If
  `NA`,  the scaling and shift factors used in the
  likelihood ratio test will be computed internally. If supplied,
  it should be a list with two scalar elements, `c_r`
  and `c_rb`, the scaling factor and the shift factors.

- `sf_args`:

  If `robust` is `"satorra.2000"` and `sf_full`
  is `NA`, this is a named list of arguments to be passed
  to `semlbci:::scaling_factor3()`, an internal function
  for computing the scaling and shift factors proposed
  by @asparouhov_simple_2010.

- `try_k_more_times`:

  How many more times to try if the
  status code is not zero.
  Default is 0 but `semlbci::semlbci()` set this argument
  to 2 when calling this function. If set to an
  integer greater than zero,
  it will call the low level function until the status
  code is zero or until this number of additional calls
  have been attempted. In each successive call, some values
  will be modified to do the search using these new
  settings.

## `semlbci::ci_bound_wn_i()`

`semlbci::ci_bound_wn_i()` is the low level function called
by `semlbci::ci_i_one()`. This function implements the
modified Wu-Neale method presented by @pek_profile_2015,
named Wu-Neale-Pek-Wu (WNPW) method in this document.
This function is not supposed to be used by users and the
interface is not user-friendly. Interested users
can refer to `vignette("technical_searching_one_bound", package = "semlbci")`
to see how to use `semlbci::ci_bound_wn_i()`
directly.

These are the main arguments of `semlbci::ci_bound_wn_i()`:

- `i`:

  The position (row number) of the target parameters
  as appeared in the parameter table of the output of
  `lavaan::lavaan()` and its wrappers, such as
  `lavaan::sem()` and `lavaan::cfa()`. This id uniquely
  identifies a parameter, which can be free, fixed, or
  user-defined.

- `npar`:

  The number of free parameters in the model,
  including those constrained to be equal. To be supplied
  by `semlbci::ci_i_one()`.

- `sem_out`:

  A `lavaan`-class object. the output of
  `lavaan::lavaan()` and its wrappers, such as
  `lavaan::sem()` and `lavaan::cfa()`.

- `f_constr`:

  The constraint function generated by
  `set_constraint()`. Created by `semlbci::semlbci()`
  and then passed to it through `semlbci::ci_i_one()`.

- `which`:

  Either `"lbound"` or `"ubound"`, denoting
  lower bound and upper bound, respectively. The confidence
  bound (limit) to be searched.

- `perturbation_factor`:

  The number by which the
  parameter estimates in `sem_out` will be multiplied,
  to set the starting values, because using the parameter
  estimates as starting values may lead to errors in the
  first few iterations. Default is .90. This argument is
  ignored if `wald_ci_start`, described below, is `TRUE`.

- `lb_var`:

  The lower bound for free parameters that are
  variances. If equal to `-Inf`, the default, `lb_prop` and
  `lb_se_k`, described below, will be used to set the lower
  bounds for free variances. If it is a number, it will be
  used to set the lower bounds for all free variances.

- `wald_ci_start`:

  If `TRUE`, there are no equality
  constraints in the model, and the target parameter is not
  a user-defined parameter, the Wald or delta confidence
  bounds will
  be used as the starting values.

- `standardized`:

  Logical. Whether the confidence bound
  of the parameter in the standardized solution is to be
  searched. For example, for a covariance, whether the
  covariance, or the correlation, is to be used in searching
  the bound. Default is `FALSE`.

- `opts`:

  A named list of options to be passed to
  `nloptr::nloptr()`, the function used for the optimization.
  Default is `list()`. This argument can be used to override
  internal settings used by `semlbci::ci_bound_wn_i()`.

- `ciperc`:

  The intended coverage probability for the
  confidence interval. Default is .95, and the bound for
  a 95% likelihood-based confidence interval will be sought.

- `ci_limit_ratio_tol`:

  The tolerance for the ratio of `a` to
  `b`, where `a` is the distance between an bound of an LBCI
  and the point estimate, and the `b` is the distance
  between the original confidence bound (by default the Wald
  or delta CI in `lavaan::lavaan()`) and the point estimate.
  If the ratio
  is larger than this value or smaller than the reciprocal
  of this value, a warning is set in the status code.
  Default is 1.5.

- `verbose`:

  If `TRUE`, the function will store more
  diagnostic information in the attribute `diag`. Default
  is `FALSE`.

- `sf`:

  A scaling factor. Used for robust confidence bounds.
  Default is 1. Precomputed by an internal function called by
  `semlbci::semlbci()` or `semlbci::ci_i_one()` when
  `robust = "satorra.2000"`.

- `sf2`:

  A shift factor. Used for robust confidence bounds.
  Default is 1. Precomputed by an internal function called by
  `semlbci::semlbci()` or `semlbci::ci_i_one()` when
  `robust = "satorra.2000"`.

- `p_tol`:

  The tolerance for checking the achieved level of
  confidence, that is, the *p*-value of the likelihood
  ratio test between the original model and the model with
  the parameter fixed to the bound found. If the absolute
  difference between the achieved level and `ciperc` is
  greater than this number, a warning is set in the status
  code and the bound is set to `NA`. Default is 5e-4.

- `xtol_rel_factor`:

  Multiply the internal default value
  of `xtol_rel` for `nloptr::nloptr()` (1.0e-5) by
  this number, usually a positive number equal to or less
  than 1,
  to change the default termination criterion. Default is 1.
  This allows tweaking the settings for optimization without
  knowing the internal default value.

- `ftol_rel_factor`:

  Multiply the internal default value
  of `ftol_rel` for `nloptr::nloptr()` (1.0e-5) by this
  number,
  usually a positive number equal to or less than 1, to
  change the default termination criterion. Default is 1.
  This allows tweaking the settings for optimization without
  knowing the internal default value.

- `lb_prop`:

  Used by an internal function to set the lower
  bound for free variances. Default is .05, setting the
  lower bound to (.05)(point estimate). Used only if the
  lower bound set by `lb_se_k` is negative. This constraint
  is used only in the optimization to prevent intermediate values
  too far away from the point estimates. The final check done
  by fitting the model in `lavaan` will not implement this
  constraint.

- `lb_se_k`

  Used by an internal function to set the lower bound
  for free variances. Default is 3, the estimate minus
  3 $\times$ standard error. If negative, the lower bound is set
  using `lb_prop`. This constraint
  is used only in the optimization to prevent intermediate values
  too far away from the point estimates. The final check done
  by fitting the model in `lavaan` will not implement this
  constraint.

Please refer to the help page of `semlbci::ci_bound_wn_i()`
to learn about other arguments.

# References
